Neural Models for Target-Based Computer-Assisted Musical Orchestration

### 2020-08-18 paper/aimusic2020/paper.tex
Fixed errors and merged figures to reduce length

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{url}
\usepackage{apacite}
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

@@

%The instruments and ranges over which they were recorded are summarized in table \ref{tab:ranges}.

@@

%CNNs show good performance on classification problems for their ability to extract spatial features, and have shown success in audio classification \cite{Hershey17}. LSTM units provide a way to learn long term dependencies in the data \cite{Hochreiter97}, which is relevant given the sequential nature of audio.

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{../latex/figs/Acc_vs_N_CNN.png}
\caption{Best overall accuracy and for each instrument obtained by the CNN with LSTM depending on the number of instruments in the combinations. \label{best_acc_cnn}}
\end{center}
\end{figure}

@@

%\begin{equation}
%M_N(\hat{X})_i = \left\{\begin{array}{ll}
%1 \text{ if } i \in I_N(\hat{X})\\
%0 \text{ otherwise}
%\end{array}\right.
%\label{NMax}
%\end{equation}
and $I_N(\hat{X})$ is the set of indices containing the $N$ first maximums of the vector $\hat{X}$.

@@

%Fig. \ref{best_acc_cnn} and Fig. \ref{best_acc_resnet} show the maximum accuracy computed using the function $f$ from Eqn. \eqref{eval}. For ResNet, the variance in accuracy is much smaller until $N$ reaches 5, at which point it becomes similar to the CNN. The results on both figures show consistency on the relative accuracy of instruments, which was for us the first step towards the validation of this method. Flute, Trombone and Trumpet yield the worst results for both models.

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.40]{../latex/figs/Acc_vs_N_ResNet.png}
\caption{Best overall accuracy and for each instrument obtained by the ResNet depending on the number of instruments in the combinations. \label{best_acc_resnet}}
\end{center}
\end{figure}

@@

\begin{table*}
  \begin{center}
    \label{orch_eval}
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|c}
     \hline
      \textbf{Model} & \textbf{Ob + Bn} & \textbf{Bn} & \textbf{Bass cl.} & \textbf{Bell 1} & \textbf{Bell 2} & \textbf{Multiph. 1} & \textbf{Car horn} & \textbf{Boat} $\ldots$ \\
      \hline
      CNN with LSTM & 0.17 & 0.28 & 0.70 & 0.55 & 0.26 & \textbf{1.10} & 0.68 & \textbf{1.12} $\ldots$  \\
      \hline
      ResNet & 0.34 & 0.50 & 0.48 & 0.59 & 0.45 & 0.90 & 0.49 & \textbf{1.16} $\ldots$ \\
      \hline
      \hline
      \textbf{$\ldots$} & \textbf{Wind harp} & \textbf{Chord 1} & \textbf{Multiph. 2} & \textbf{Chord 2} & \textbf{Gong} & \textbf{Scream} & \textbf{Brass} & \textbf{Average}  \\
      \hline
      $\ldots$ & 0.55 & 0.79 & 0.70 & 0.57 & 0.73 & \textbf{1.14} & 0.79 & 0.71\\
      \hline
      $\ldots$  & 0.61 & 0.86 & 0.51 & 0.37 & 0.71 & \textbf{1.03} & \textbf{1.05} & 0.66 \\
      \hline
    \end{tabular}
  \end{center}
%  \caption{Quantitative comparison of orchestrations as ratios to Orchidea. Eqn. \eqref{distance} was used with $\lambda_1 = 0.5$ and $\lambda_2 = 10$ to compute distances between orchestrations and targets. What is shown is the ratio between the distance calculated and Orchidea's distance for the same target. A value less than 1 means that the model performed worse (i.e. had a larger distance), and a value greater than 1 means the model performed better than Orchidea. The last column shows the ratio of the average distances for the model across all targets.}
\end{table*}

@@

%For quantitative evaluation, we used the distance metric defined in Eqn. \eqref{distance} to calculate differences in timbre between targets and solutions. This metric is proposed in \cite{Cella2020} as part of the cost function used in Orchidea during the optimization. The equation takes in the full FFT of the target $x$ and full FFT of the solution $\hat{x}$. Then for each bin $k$ of the FFT, it calculates the absolute difference between the values. The differing values of $\lambda_1$ and $\lambda_2$ allow the metric to penalize the solution in different ways.

@@

\begin{equation}\label{distance}
d(x, \tilde{x}) =\lambda_1 \sum_k \delta_{k1}(x_k - \tilde{x}_k) + \lambda_2 \sum_k \delta_{k2}|x_k - \tilde{x	}_k| \\
\end{equation}
where 
%$
%\delta_{k1} = 
%\begin{cases}
%1, \text{if   } x_k \ge \tilde{x}_k \\
%0, \text{otherwise}
%\end{cases} 
%$, $
%\delta_{k2} = 
%\begin{cases}
%1, \text{if   } x_k < \tilde{x}_k \\
%0, \text{otherwise}
%\end{cases}.
%$\\

>>>>

\usepackage{amssymb}
\usepackage{amsmath}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{url}
\usepackage{apacite}
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

@@

The instruments and ranges over which they were recorded are summarized in table \ref{tab:ranges}.

@@

CNNs show good performance on classification problems for their ability to extract spatial features, and have shown success in audio classification \cite{Hershey17}. LSTM units provide a way to learn long term dependencies in the data \cite{Hochreiter97}, which is relevant given the sequential nature of audio.

@@

@@

\begin{equation}
M_N(\hat{X})_i = \left\{\begin{array}{ll}
1 \text{ if } i \in I_N(\hat{X})\\
0 \text{ otherwise}
\end{array}\right.
\label{NMax}
\end{equation}
and $I_N(\hat{X})$ is the set of indices containing the $N$ first maximums of the vector $\hat{X}$.

@@

Fig. \ref{best_acc_cnn} and Fig. \ref{best_acc_resnet} show the maximum accuracy computed using the function $f$ from Eqn. \ref{eval}. For ResNet, the variance in accuracy is much smaller until $N$ reaches 5, at which point it becomes similar to the CNN. The results on both figures show consistency on the relative accuracy of instruments, which was for us the first step towards the validation of this method. Flute, Trombone and Trumpet yield the worst results for both models.

@@

\begin{figure}
\centering
\begin{subfigure}{.65\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{../latex/figs/Acc_vs_N_CNN.png}
  \caption{CNN with LSTM}
  \label{best_acc_cnn}
\end{subfigure}%
\begin{subfigure}{.65\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{../latex/figs/Acc_vs_N_ResNet.png}
  \caption{ResNet}
  \label{best_acc_resnet}
\end{subfigure}
\caption{Best overall accuracy and for each instrument obtained by the CNN with LSTM and the ResNet depending on the number of instruments in the combinations}
\end{figure}

@@

\begin{table*}
  \begin{center}
    \label{orch_eval}
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|c}
     \hline
      \textbf{Model} & \textbf{Ob + Bn} & \textbf{Bn} & \textbf{Bass cl.} & \textbf{Bell 1} & \textbf{Bell 2} & \textbf{Multiph. 1} & \textbf{Car horn} & \textbf{Boat} $\ldots$ \\
      \hline
      CNN with LSTM & 0.17 & 0.28 & 0.70 & 0.55 & 0.26 & \textbf{1.10} & 0.68 & \textbf{1.12} $\ldots$  \\
      \hline
      ResNet & 0.34 & 0.50 & 0.48 & 0.59 & 0.45 & 0.90 & 0.49 & \textbf{1.16} $\ldots$ \\
      \hline
      \hline
      \textbf{$\ldots$} & \textbf{Wind harp} & \textbf{Chord 1} & \textbf{Multiph. 2} & \textbf{Chord 2} & \textbf{Gong} & \textbf{Scream} & \textbf{Brass} & \textbf{Average}  \\
      \hline
      $\ldots$ & 0.55 & 0.79 & 0.70 & 0.57 & 0.73 & \textbf{1.14} & 0.79 & 0.71\\
      \hline
      $\ldots$  & 0.61 & 0.86 & 0.51 & 0.37 & 0.71 & \textbf{1.03} & \textbf{1.05} & 0.66 \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Quantitative comparison of orchestrations as ratios to Orchidea. Eqn. \ref{distance} was used with $\lambda_1 = 0.5$ and $\lambda_2 = 10$ to compute distances between orchestrations and targets. What is shown is the ratio between the distance calculated and Orchidea's distance for the same target. A value less than 1 means that the model performed worse (i.e. had a larger distance), and a value greater than 1 means the model performed better than Orchidea. The last column shows the ratio of the average distances for the model across all targets.}
\end{table*}

@@

For quantitative evaluation, we used the distance metric defined in Eqn. \ref{distance} to calculate differences in timbre between targets and solutions. This metric is proposed in \cite{Cella2020} as part of the cost function used in Orchidea during the optimization. The equation takes in the full FFT of the target $x$ and full FFT of the solution $\hat{x}$. Then for each bin $k$ of the FFT, it calculates the absolute difference between the values. The differing values of $\lambda_1$ and $\lambda_2$ allow the metric to penalize the solution in different ways.

@@

\begin{equation}\label{distance}
d(x, \tilde{x}) =\lambda_1 \sum_k \delta_{k1}(x_k - \tilde{x}_k) + \lambda_2 \sum_k \delta_{k2}|x_k - \tilde{x	}_k| \\
\end{equation}
where 
$
\delta_{k1} = 
\begin{cases}
1, \text{if   } x_k \ge \tilde{x}_k \\
0, \text{otherwise}
\end{cases} 
$, $
\delta_{k2} = 
\begin{cases}
1, \text{if   } x_k < \tilde{x}_k \\
0, \text{otherwise}
\end{cases}.
$\\
